\NeedsTeXFormat{LaTeX2e}

\newcommand*{\Title}{Overview}
\newcommand*{\CTANdir}{macros/latex/contrib/oberdiek/}
\newcommand*{\CTANroot}{http://mirror.ctan.org/}
\newcommand*{\CTANpkg}[1]{%
  \href{http://ctan.org/pkg/#1}{[ctan]}%
}
\newcommand*{\Subject}{CTAN:\CTANdir}
\newcommand*{\Author}{Heiko Oberdiek}

\newcommand*{\Email}{ho-tex at tug.org}
\newcommand*{\Date}{2019/12/15}

% Copyright (C) 2006-2016 by
%    Heiko Oberdiek
% Copyright (C) 2016-2019 by
%    Oberdiek Package Support Group
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either
% version 1.3 of this license or (at your option) any later
% version. The latest version of this license is in
%    http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of
% LaTeX version 2003/12/01 or later.
%
% This work has the LPPL maintenance status "maintained".
%
% This Current Maintainer of this work is the Oberdiek Package Support Group.
%
% This work consists of the overview "oberdiek.pdf", its source
% "oberdiek.tex", and the installation script "oberdiek.ins"
% for the projects in CTAN:macros/latex/contrib/oberdiek/.
%
\documentclass[a4paper,12pt]{article}

\usepackage{iftex}
\ifluatex
  \usepackage{unicode-math}[2011/09/19]%
\fi

\usepackage[
  ignorehead,
  top=1in,
]{geometry}
\usepackage{longtable}
\usepackage{color}
\usepackage[ngerman,english]{babel}
\usepackage{hologo}
\usepackage{biblatex}% for internals in .toc files

\definecolor{link}{rgb}{1,0,0}% red
\definecolor{file}{rgb}{0,0,1}% blue
\definecolor{url}{cmyk}{0.1,1,0,0.1}

\definecolor{file}{rgb}{1,0,0}% red
\definecolor{url}{rgb}{0,0,1}% blue
\definecolor{link}{rgb}{0,0.75,0}%

\usepackage[
  colorlinks,
]{hyperref}[2006/02/12]
\hypersetup{
  pdftitle={CTAN:\CTANdir},
  pdfsubject={Package Overview},
  pdfauthor={\Author\ <\Email>},
  bookmarksnumbered,
  bookmarksopen,
  bookmarksopenlevel=2,
  bookmarksdepth=2,
  filecolor=file,
  urlcolor=url,
  linkcolor=link,
}
\usepackage{bookmark}
\usepackage{hypdestopt}
\setcounter{tocdepth}{1}
\setcounter{secnumdepth}{1}

\title{%
  \href{\CTANroot\CTANdir}{CTAN:\CTANdir}%
}
\author{%
  \Author\thanks
 {Please report any issues at \url{https://github.com/ho-tex/oberdiek/issues}}\\
  \textless
  \href{mailto:\Email}{\texttt{\Email}}%
  \textgreater
}
\date{\Date}

\providecommand*{\pdfTeX}{pdf\TeX}
\providecommand*{\plainTeX}{\mbox{plain-\TeX}}
\providecommand*{\iniTeX}{\mbox{ini-\TeX}}
\providecommand*{\VTeX}{V\TeX}
\providecommand*{\eTeX}{$\csname m@th\endcsname\varepsilon$-\TeX}
\providecommand*{\LuaTeX}{%
  L\textsc{ua}\TeX
}
\newcommand*{\xpackage}[1]{\textsf{#1}}
\newcommand*{\xmodule}[1]{\textsf{#1}}
\newcommand*{\xfile}[1]{\texttt{#1}}
\newcommand*{\xext}[1]{\texttt{.#1}}
\newcommand*{\xoption}[1]{\textsf{#1}}
\newcommand*{\cs}[1]{\texttt{\textbackslash#1}}
\newcommand*{\meta}[1]{%
  \ensuremath\langle
  \textit{#1}%
  \ensuremath\rangle
}

\makeatletter
\g@addto@macro\abstract{\noindent\ignorespaces}

\newcommand*{\tocinclude}[1]{%
  \setcounter{tocdepth}{3}%
  \begingroup
    \makeatletter
    \def\@prj{#1}%
    \let\contentsline\foreign@contentsline
    \input{\@prj.toc}%
  \endgroup
}
\def\foreign@contentsline#1#2#3#4{%
  \ifx\\#4\\%
    \csname l@#1\endcsname{#2}{#3}%
  \else
    \ifHy@linktocpage
      \csname l@#1\endcsname{{#2}}{%
        \hyper@linkfile{#3}{\@prj.pdf}{#4}%
      }%
    \else
      \csname l@#1\endcsname{%
        \hyper@linkfile{#2}{\@prj.pdf}{#4}%
      }{#3}%
    \fi
  \fi
}%

\newenvironment{overview}{%
  \setlength{\tabcolsep}{0.8\tabcolsep}%
  \setlength{\LTleft}{0pt}%
  \longtable{@{}lll@{}}
}{%
  \endlongtable
}
\newcommand*{\entry}[2]{%
  \href{file:#1.pdf}{%
    \bfseries\xpackage{#1}%
  }%
   &
    #2%
  & \CTANpkg{#1} %
  \\*%
  \hyperref[{#1}]{\small (contents)}%
  &
  \\%
}
\newcommand*{\entrysep}{1.5ex}

\newcommand*{\pkgsectformat}[1]{%
  \texorpdfstring{%
    \textcolor{link}{The} %
    \xpackage{#1} %
    \textcolor{link}{package}%
  }{#1}%
}

\makeatother

\begin{document}
\maketitle

\section{Overview}
\begin{overview}
\entry{aliascnt}{Alias counters}%
[\entrysep]
\entry{bmpsize}{Extract size/resolution from bitmap files}%
[\entrysep]
\entry{centernot}{Centers the not symbol horizontally}%
[\entrysep]
\entry{chemarr}{Arrows for chemical reactions}%
[\entrysep]
\entry{classlist}{Record classes used in a document}%
[\entrysep]
\entry{colonequals}{Colon equals symbols}%
[\entrysep]
\entry{dvipscol}{Alter the usage of the dvips color stack}%
[\entrysep]
\entry{engord}{Provides English ordinal numbers}%
[\entrysep]
\entry{enparen}{Parentheses nesting}%
[\entrysep]
\entry{eolgrab}{Catch arguments delimited by end of line}%
[\entrysep]
\entry{fibnum}{Fibonacci numbers}%
[\entrysep]
\entry{flags}{Setting/clearing of flags in bit fields}%
[\entrysep]
\entry{holtxdoc}{Private additional ltxdoc support}%
[\entrysep]
\entry{hopatch}{Wrapper for package hooks}%
[\entrysep]
\entry{hypbmsec}{Bookmarks in sectioning commands}%
[\entrysep]
\entry{hypcap}{Adjusting the anchors of captions}%
[\entrysep]
\entry{hypdestopt}{Hyperref destination optimizer}%
[\entrysep]
\entry{hypdoc}{Hyper extensions for doc.sty}%
[\entrysep]
\entry{hypgotoe}{Links to embedded files}%
[\entrysep]
\entry{hyphsubst}{Substitute hyphenation patterns}%
[\entrysep]
\entry{ifdraft}{Detect class options draft and final}%
[\entrysep]
\entry{iflang}{Checks for the current language}%
[\entrysep]
\entry{pagegrid}{Print page grid in background}%
[\entrysep]
\entry{pagesel}{Select pages of a document for output}%
[\entrysep]
\entry{pdfcol}{Handle new color stacks for \hologo{pdfTeX}}%
[\entrysep]
\entry{pdfcolfoot}{Color stack for footnotes with \hologo{pdfTeX}}%
[\entrysep]
\entry{pdfcolparallel}{Color stacks support for parallel}%
[\entrysep]
\entry{pdfcolparcolumns}{Color stacks for parcolumns}%
[\entrysep]
\entry{pdfcrypt}{Allows the setting of PDF encryption}%
[\entrysep]
\entry{pdfrender}{Access to some PDF graphics parameters}%
[\entrysep]
\entry{protecteddef}{Define protected commands}%
[\entrysep]
\entry{resizegather}{Resize overly large equations}%
[\entrysep]
\entry{rotchiffre}{Perform simple rotation ciphers}%
[\entrysep]
\entry{scrindex}{Package index with \hologo{KOMAScript} classes}%
[\entrysep]
\entry{setouterhbox}{Set hbox in outer horizontal mode}%
[\entrysep]
\entry{settobox}{Assign box dimensions to length registers}%
[\entrysep]
\entry{stackrel}{Adding subscript option to stackrel}%
[\entrysep]
\entry{stampinclude}{Include files based on time stamps}%
[\entrysep]
\entry{tabularht}{Tabular with height specified}%
[\entrysep]
\entry{tabularkv}{Tabular with key value interface}%
[\entrysep]
\entry{telprint}{Format German phone numbers}%
[\entrysep]
\entry{thepdfnumber}{Print PDF numbers with minimal digits}%
[\entrysep]
\entry{twoopt}{Definitions with two optional arguments}%
\end{overview}

\section{Packages}
\hypersetup{bookmarksnumbered=false}

\subsection{\pkgsectformat{aliascnt}}
\label{aliascnt}
\begin{abstract}
Package \xpackage{aliascnt} introduces \emph{alias counters} that
share the same counter register and clear list.
\end{abstract}
\tocinclude{aliascnt}

\newpage
\subsection{\pkgsectformat{bmpsize}}
\label{bmpsize}
\begin{abstract}
Package \xpackage{bmpsize} analyzes bitmap images to extract
size and resolution data. It adds this feature to the graphics package
that now do not need separate bounding box files for bitmap images.
Additionally the implementation for the inclusion of bitmap images
in some drivers of package \xpackage{graphicx} are rewritten to support
options \xoption{viewport}, \xoption{trim} and \xoption{clip}.
\end{abstract}
\tocinclude{bmpsize}

\newpage
\subsection{\pkgsectformat{centernot}}
\label{centernot}
\begin{abstract}
This package provides \cs{centernot} that prints the symbol
\cs{not} on the following argument. Unlike \cs{not} the symbol
is horizontally centered.
\end{abstract}
\tocinclude{centernot}

\newpage
\subsection{\pkgsectformat{chemarr}}
\label{chemarr}
\begin{abstract}
Very often chemists need a longer version
of reaction arrows (\cs{rightleftharpoons}) with
the possibility to put text above and below.
Analogous to \xpackage{amsmath}'s \cs{xrightarrow} and
\cs{xleftarrow} this package provides the macro
\cs{xrightleftharpoons}.
\end{abstract}
\tocinclude{chemarr}

\newpage
\subsection{\pkgsectformat{classlist}}
\label{classlist}
\begin{abstract}
This package records the loaded classes and stores
them in a list.
\end{abstract}
\tocinclude{classlist}

\newpage
\subsection{\pkgsectformat{colonequals}}
\label{colonequals}
\begin{abstract}
Package \xpackage{colonequals} defines poor man's symbols
for math relation symbols such as ``colon equals''.
The colon is centered around the horizontal math axis.
\end{abstract}
\tocinclude{colonequals}

\newpage
\subsection{\pkgsectformat{dvipscol}}
\label{dvipscol}
\begin{abstract}
Color support for dvips in \xfile{dvips.def} involves the
color stack of dvips. The package tries to remove unnecessary
uses of the stack to avoid the error ``out of coor stack space''.
\end{abstract}
\tocinclude{dvipscol}


\newpage
\subsection{\pkgsectformat{engord}}
\label{engord}
\begin{abstract}
The package generates the suffix of English ordinal numbers.
It can be used with plain and \LaTeX\ formats.
\end{abstract}
\tocinclude{engord}

\newpage
\subsection{\pkgsectformat{enparen}}
\label{enparen}
\begin{abstract}
The package defines macros to set parentheses that automatically
change the symbols from inner to outer fences.
\end{abstract}
\tocinclude{enparen}

\newpage
\subsection{\pkgsectformat{eolgrab}}
\label{eolgrab}
\begin{abstract}
This package implements a generic argument grabber
to catch an argument that is delimited by the line end.
\end{abstract}
\tocinclude{eolgrab}

\newpage
\subsection{\pkgsectformat{fibnum}}
\label{fibnum}
\begin{abstract}
The package \xpackage{fibnum} provides expandable fibonacci
numbers for both \hologo{LaTeX} and \hologo{plainTeX}.
\end{abstract}
\tocinclude{fibnum}

\newpage
\subsection{\pkgsectformat{flags}}
\label{flags}
\begin{abstract}
Package \xpackage{flags} allows the setting and clearing
of flags in bit fields and converts the bit field into a
decimal number. Currently the bit field is limited to 31 bits.
\end{abstract}
\tocinclude{flags}

\newpage
\subsection{\pkgsectformat{holtxdoc}}
\label{holtxdoc}
\begin{abstract}
The package is used for the documentation of my packages in
DTX format. It contains some private macros and setup for
my needs. Thus do not use it. I have separated the part
that may be useful for others in package \xpackage{hypdoc}.
\end{abstract}
\tocinclude{holtxdoc}

\newpage
\subsection{\pkgsectformat{hopatch}}
\label{hopatch}
\begin{abstract}
This packages provides a wrapper to various package hooks
provided by other packages or classes, but does not define
own hooks.
\end{abstract}
\tocinclude{hopatch}

\newpage
\subsection{\pkgsectformat{hypbmsec}}
\label{hypbmsec}
\begin{abstract}
This package expands the syntax of the sectioning commands. If the
argument of the sectioning commands isn't usable as outline entry,
a replacement for the bookmarks can be given.
\end{abstract}
\tocinclude{hypbmsec}

\newpage
\subsection{\pkgsectformat{hypcap}}
\label{hypcap}
\begin{abstract}
This package tries a solution of the problem with
hyperref, that links to floats points below the
caption and not at the beginning of the float.
Therefore this package divides the task into two
part, the link setting with \cs{capstart} or
automatically at the beginning of a float and
the rest in the \cs{caption} command.
\end{abstract}
\tocinclude{hypcap}

\newpage
\subsection{\pkgsectformat{hypdestopt}}
\label{hypdestopt}
\begin{abstract}
Package \xpackage{hypdestopt} supports \xpackage{hyperref}'s
\xoption{pdftex} driver. It removes unnecessary destinations
and shortens the destination names or uses numbered destinations
to get smaller PDF files.
\end{abstract}
\tocinclude{hypdestopt}

\newpage
\subsection{\pkgsectformat{hypdoc}}
\label{hypdoc}
\begin{abstract}
This package adds hyper features to the package
\xpackage{doc} that is used in the documentation
system of \LaTeXe. Bookmarks are added and references
are linked as far as possible.
\end{abstract}
\tocinclude{hypdoc}

\newpage
\subsection{\pkgsectformat{hypgotoe}}
\label{hypgotoe}
\begin{abstract}
Experimental package for links to embedded files.
\end{abstract}
\tocinclude{hypgotoe}

\newpage
\subsection{\pkgsectformat{hyphsubst}}
\label{hyphsubst}
\begin{abstract}
A \TeX\ format file may include alternative hyphenation patterns
for a language with a different name. If the naming convention
follows \xpackage{babel's} rules, then the hyphenation patterns
for a language can be replaced by the alternative hyphenation patterns,
provided in the format file.
\end{abstract}
\tocinclude{hyphsubst}

\newpage
\subsection{\pkgsectformat{ifdraft}}
\label{ifdraft}
\begin{abstract}
The package provides an interface for selecting code depending
on the options \xoption{draft} and \xoption{final}.
\end{abstract}
\tocinclude{ifdraft}

\newpage
\subsection{\pkgsectformat{iflang}}
\label{iflang}
\begin{abstract}
This package provides expandible checks for the current language
based on macro \cs{languagename} or hyphenation patterns.
\end{abstract}
\tocinclude{iflang}

\newpage
\subsection{\pkgsectformat{pagegrid}}
\label{pagegrid}
\begin{abstract}
The \LaTeX\ package prints a page grid in the background.
\end{abstract}
\tocinclude{pagegrid}

\newpage
\subsection{\pkgsectformat{pagesel}}
\label{pagesel}
\begin{abstract}
Single pages or page areas can be selected for output.
\end{abstract}
\tocinclude{pagesel}

\newpage
\subsection{\pkgsectformat{pdfcol}}
\label{pdfcol}
\begin{abstract}
Since version 1.40 \pdfTeX\ supports color stacks.
The driver file \xfile{pdftex.def} for package \xpackage{color}
defines and uses a main color stack since version v0.04b.
Package \xpackage{pdfcol} is intended for package writers.
It defines macros for setting and maintaining new color stacks.
\end{abstract}
\tocinclude{pdfcol}

\newpage
\subsection{\pkgsectformat{pdfcolfoot}}
\label{pdfcolfoot}
\begin{abstract}
Since version 1.40 \pdfTeX\ supports several color stacks. This
package uses a separate color stack for footnotes that can break
across pages.
\end{abstract}
\tocinclude{pdfcolfoot}

\newpage
\subsection{\pkgsectformat{pdfcolparallel}}
\label{pdfcolparallel}
\begin{abstract}
This packages fixes bugs in \xpackage{parallel} and
improves color support by using several color stacks
that are provided by \pdfTeX\ since version 1.40.
\end{abstract}
\tocinclude{pdfcolparallel}

\newpage
\subsection{\pkgsectformat{pdfcolparcolumns}}
\label{pdfcolparcolumns}
\begin{abstract}
Since version 1.40 \pdfTeX\ supports several color stacks.
This package uses them to fix color problems in
package \xpackage{parcolumns}.
\end{abstract}
\tocinclude{pdfcolparcolumns}

\newpage
\subsection{\pkgsectformat{pdfcrypt}}
\label{pdfcrypt}
\begin{abstract}
This package supports the setting of pdf encryption options
for \VTeX\ and some older versions of \pdfTeX.
\end{abstract}
\tocinclude{pdfcrypt}

\newpage
\subsection{\pkgsectformat{pdfrender}}
\label{pdfrender}
\begin{abstract}
The PDF format has some graphics parameter like
line width or text rendering mode. This package
provides an interface for setting these parameters.
\end{abstract}
\tocinclude{pdfrender}


\newpage
\subsection{\pkgsectformat{protecteddef}}
\label{protecteddef}
\begin{abstract}
This packages provides \cs{ProtectedDef} for defining
robust macros for both \hologo{plainTeX} and \hologo{LaTeX}.
First \hologo{eTeX}'s \cs{protected} is tried, then
\hologo{LaTeX}'s \cs{DeclareRobustCommand} is used.
Otherwise the macro is not made robust.
\end{abstract}
\tocinclude{protecteddef}

\newpage
\subsection{\pkgsectformat{resizegather}}
\label{resizegather}
\begin{abstract}
Equations that are too large are resized to fit the available
space. The environment \textsf{gather} of package \xpackage{amsmath}
is supported. Also the environments \textsf{equation} and
\textsf{displaymath} are redefined using \textsf{gather}
and its starred version.
\end{abstract}
\tocinclude{resizegather}

\newpage
\subsection{\pkgsectformat{rotchiffre}}
\label{rotchiffre}
\begin{abstract}
This package implements chiffres ROT13 with its variants
ROT5, ROT18, and ROT47.
\end{abstract}
\tocinclude{rotchiffre}

\newpage
\subsection{\pkgsectformat{scrindex}}
\label{scrindex}
\begin{abstract}
This package redefines environment `theindex' of package \xpackage{index},
if a class from KOMA-Script is loaded. Also option \xoption{idxtotoc}
is supported. Index preambles can be given either by means of package
\xpackage{index} or via the interface provided by KOMA-Script.
\end{abstract}
\tocinclude{scrindex}

\newpage
\subsection{\pkgsectformat{setouterhbox}}
\label{setouterhbox}
\begin{abstract}
If math stuff is set in an \cs{hbox}, then TeX
performs some optimization and omits the implicite
penalties \cs{binoppenalty} and \cs{relpenalty}.
This packages tries to put stuff into an \cs{hbox}
without getting lost of those penalties.
\end{abstract}
\tocinclude{setouterhbox}

\newpage
\subsection{\pkgsectformat{settobox}}
\label{settobox}
\begin{abstract}
Commands are defined for getting box sizes similar
to \LaTeX's \cs{settowidth} commands.
\end{abstract}
\tocinclude{settobox}

\newpage
\subsection{\pkgsectformat{stackrel}}
\label{stackrel}
\begin{abstract}
This package adds an optional argument to \cs{stackrel} for
putting something below the relational symbol and defines
\cs{stackbin} for binary symbols.
\end{abstract}
\tocinclude{stackrel}

\newpage
\subsection{\pkgsectformat{stampinclude}}
\label{stampinclude}
\begin{abstract}
The package replaces \cs{includeonly} and selects the files for
\cs{include} by inspecting the time stamp of the \xext{aux} file.
The file is selected for inclusion if the \xext{aux} file does
not yet exist or is older than the corresponding \xext{tex} file.
\end{abstract}
\tocinclude{stampinclude}

\newpage
\subsection{\pkgsectformat{tabularht}}
\label{tabularht}
\begin{abstract}
This package defines some environments that adds
a height specification to tabular and array.
\end{abstract}
\tocinclude{tabularht}

\newpage
\subsection{\pkgsectformat{tabularkv}}
\label{tabularkv}
\begin{abstract}
This package adds a key value interface for tabular
by the new environment \texttt{tabularkv}. Thus the
\TeX\ source code looks better by named parameters,
especially if package \xpackage{tabularht} is used.
\end{abstract}
\tocinclude{tabularkv}

\newpage
\subsection{\pkgsectformat{telprint}}
\label{telprint}
\begin{abstract}
Package \xpackage{telprint} provides \cs{telprint} for formatting
German phone numbers.
\end{abstract}
\tocinclude{telprint}

\newpage
\subsection{\pkgsectformat{thepdfnumber}}
\label{thepdfnumber}
\begin{abstract}
The package converts real numbers to a minimal representation
that is stripped from leading or trailing zeros,
plus signs and decimal point if not necessary.
\end{abstract}
\tocinclude{thepdfnumber}


\newpage
\subsection{\pkgsectformat{twoopt}}
\label{twoopt}
\begin{abstract}
This package provides commands to define macros with two
optional arguments.
\end{abstract}
\tocinclude{twoopt}


\end{document}
