\NeedsTeXFormat{LaTeX2e}

\newcommand*{\Title}{Overview}
\newcommand*{\CTANdir}{macros/latex/contrib/ho-latex/}
\newcommand*{\CTANroot}{ftp://ftp.ctan.org/tex-archive/}
\newcommand*{\Subject}{CTAN:\CTANdir}
\newcommand*{\Author}{Heiko Oberdiek}
\newcommand*{\Email}{ho-tex at tug.org}
\newcommand*{\Date}{2019/07/25}

% Copyright (C) 2006-2019 by
%    Heiko Oberdiek <heiko.oberdiek at googlemail.com>
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either
% version 1.3 of this license or (at your option) any later
% version. The latest version of this license is in
%    http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of
% LaTeX version 2003/12/01 or later.
%
% This work has the LPPL maintenance status "maintained".
%
% This Current Maintainer of this work is Heiko Oberdiek.
%
% This work consists of the overview "ho-latex.pdf", its source
% "ho-latex.tex", and the installation script "ho-latex.ins"
% for the projects in CTAN:macros/latex/contrib/ho-latex/.
%
\documentclass[a4paper,12pt]{article}

\usepackage{ifluatex}
\ifluatex
  \usepackage{fontspec}[2011/09/18]%
  \usepackage{unicode-math}[2011/09/19]%
  \setmathfont{latinmodern-math.otf}%
\fi

\usepackage[
  ignorehead,
  top=1in,
]{geometry}
\usepackage{longtable}
\usepackage{color}
\usepackage[ngerman,english]{babel}
\usepackage{hologo}
\usepackage{biblatex}% for internals in .toc files

\definecolor{link}{rgb}{1,0,0}% red
\definecolor{file}{rgb}{0,0,1}% blue
\definecolor{url}{cmyk}{0.1,1,0,0.1}

\definecolor{file}{rgb}{1,0,0}% red
\definecolor{url}{rgb}{0,0,1}% blue
\definecolor{link}{rgb}{0,0.75,0}%

\usepackage[
  colorlinks,
]{hyperref}[2006/02/12]
\hypersetup{
  pdftitle={CTAN:\CTANdir},
  pdfsubject={Package Overview},
  pdfauthor={\Author\ <\Email>},
  bookmarksnumbered,
  bookmarksopen,
  bookmarksopenlevel=2,
  bookmarksdepth=2,
  filecolor=file,
  urlcolor=url,
  linkcolor=link,
}
\usepackage{bookmark}
\usepackage{hypdestopt}
\setcounter{tocdepth}{1}
\setcounter{secnumdepth}{1}

\title{%
  \href{\CTANroot\CTANdir}{CTAN:\CTANdir}%
}
\author{%
  \Author\\
  \textless
  \href{mailto:\Email}{\texttt{\Email}}%
  \textgreater
}
\date{\Date}

\providecommand*{\pdfTeX}{pdf\TeX}
\providecommand*{\plainTeX}{\mbox{plain-\TeX}}
\providecommand*{\iniTeX}{\mbox{ini-\TeX}}
\providecommand*{\VTeX}{V\TeX}
\providecommand*{\eTeX}{$\csname m@th\endcsname\varepsilon$-\TeX}
\providecommand*{\LuaTeX}{%
  L\textsc{ua}\TeX
}
\newcommand*{\xpackage}[1]{\textsf{#1}}
\newcommand*{\xmodule}[1]{\textsf{#1}}
\newcommand*{\xfile}[1]{\texttt{#1}}
\newcommand*{\xext}[1]{\texttt{.#1}}
\newcommand*{\xoption}[1]{\textsf{#1}}
\newcommand*{\cs}[1]{\texttt{\textbackslash#1}}
\newcommand*{\meta}[1]{%
  \ensuremath\langle
  \textit{#1}%
  \ensuremath\rangle
}

\makeatletter
\g@addto@macro\abstract{\noindent\ignorespaces}

\newcommand*{\tocinclude}[1]{%
  \setcounter{tocdepth}{3}%
  \begingroup
    \makeatletter
    \def\@prj{#1}%
    \let\contentsline\foreign@contentsline
    \input{\@prj.toc}%
  \endgroup
}
\def\foreign@contentsline#1#2#3#4{%
  \ifx\\#4\\%
    \csname l@#1\endcsname{#2}{#3}%
  \else
    \ifHy@linktocpage
      \csname l@#1\endcsname{{#2}}{%
        \hyper@linkfile{#3}{\@prj.pdf}{#4}%
      }%
    \else
      \csname l@#1\endcsname{%
        \hyper@linkfile{#2}{\@prj.pdf}{#4}%
      }{#3}%
    \fi
  \fi
}%

\newenvironment{overview}{%
  \setlength{\tabcolsep}{0.8\tabcolsep}%
  \setlength{\LTleft}{0pt}%
  \longtable{@{}llll@{}}
}{%
  \endlongtable
}
\newcommand*{\entry}[4]{%
  \href{file:#1.pdf}{%
    \bfseries\xpackage{#1}%
  }%
  & #2%
  & v#3%
  & \href{\CTANroot\CTANdir #1.pdf}{[pdf]} %
    \href{\CTANroot\CTANdir #1.dtx}{[dtx]}
  \\*%
  \hyperref[{#1}]{\small (contents)}%
  &
  \multicolumn{2}{l}{%
    #4%
  }%
  \\%
}
\newcommand*{\entrysep}{1.5ex}

\newcommand*{\pkgsectformat}[1]{%
  \texorpdfstring{%
    \textcolor{link}{The} %
    \xpackage{#1} %
    \textcolor{link}{package}%
  }{#1}%
}

\makeatother

\begin{document}
\maketitle

\section{Overview}
\begin{overview}
\entry{accsupp}{2010/01/16}{0.3}{Accessibility support by marked content}%
[\entrysep]
\entry{aliascnt}{2009/09/08}{1.3}{Alias counters}%
[\entrysep]
\entry{askinclude}{2011/12/02}{2.2}{Interactive asking of included files}%
[\entrysep]
\entry{atenddvi}{2007/04/17}{1.1}{At end DVI hook}%
[\entrysep]
\entry{attachfile2}{2019/07/24}{2.9}{Attach files into PDF}%
[\entrysep]
\entry{atveryend}{2011/06/30}{1.8}{Hooks at the very end of document}%
[\entrysep]
\entry{auxhook}{2011/03/04}{1.3}{Hooks for auxiliary files}%
[\entrysep]
\entry{bmpsize}{2009/09/04}{1.6}{Extract size/resolution from bitmap files}%
[\entrysep]
\entry{bookmark}{2011/12/02}{1.24}{PDF bookmarks}%
[\entrysep]
\entry{centernot}{2011/07/11}{1.3}{Centers the not symbol horizontally}%
[\entrysep]
\entry{chemarr}{2006/02/20}{1.2}{Arrows for chemical reactions}%
[\entrysep]
\entry{classlist}{2011/10/17}{1.4}{Record classes used in a document}%
[\entrysep]
\entry{colonequals}{2006/08/01}{1.0}{Colon equals symbols}%
[\entrysep]
\entry{dvipscol}{2008/08/11}{1.2}{Alter the usage of the dvips color stack}%
[\entrysep]
\entry{enparen}{2012/01/07}{1.0}{Parentheses nesting}%
[\entrysep]
\entry{epstopdf}{2010/02/09}{2.5}{Conversion with epstopdf on the fly}%
[\entrysep]
\entry{flags}{2007/09/30}{0.4}{Setting/clearing of flags in bit fields}%
[\entrysep]
\entry{grfext}{2010/08/19}{1.1}{Manage graphics extensions}%
[\entrysep]
\entry{grffile}{2012/04/05}{1.16}{Extended file name support for graphics}%
[\entrysep]
\entry{holtxdoc}{2012/03/21}{0.24}{Private additional ltxdoc support}%
[\entrysep]
\entry{hopatch}{2011/06/24}{1.1}{Wrapper for package hooks}%
[\entrysep]
\entry{ifdraft}{2008/08/11}{1.3}{Detect class options draft and final}%
[\entrysep]
\entry{inputenx}{2011/05/27}{1.10}{Enhanced input encoding handling}%
[\entrysep]
\entry{letltxmacro}{2010/09/02}{1.4}{Let assignment for \hologo{LaTeX} macros}%
[\entrysep]
\entry{listingsutf8}{2011/11/10}{1.2}{Allow UTF-8 in listings input}%
[\entrysep]
<<<<<<< HEAD:ho-latex/ho-latex.tex
\entry{luacolor}{2011/11/01}{1.8}{Color support via \hologo{LuaTeX}'s attributes}%
[\entrysep]
=======
\entry{ltxcmds}{2011/11/09}{1.22}{\hologo{LaTeX} kernel commands for general use}%
[\entrysep]
\entry{luacolor}{2019/07/25}{1.12}{Color support via \hologo{LuaTeX}'s attributes}%
[\entrysep]
\entry{luatex}{2019/07/25}{0.7}{\hologo{LuaTeX} basic definition package}%
[\entrysep]
\entry{magicnum}{2019/07/25}{1.6}{Magic numbers}%
[\entrysep]
>>>>>>> master:oberdiek.tex
\entry{makerobust}{2006/03/18}{1.0}{Make existing macro robust}%
[\entrysep]
\entry{pagegrid}{2009/12/04}{1.4}{Print page grid in background}%
[\entrysep]
\entry{pagesel}{2008/08/11}{1.8}{Select pages of a document for output}%
[\entrysep]
\entry{pdflscape}{2008/08/11}{0.10}{Display of landscape pages in PDF}%
[\entrysep]
<<<<<<< HEAD:ho-latex/ho-latex.tex
=======
\entry{pdfrender}{2010/01/28}{1.2}{Access to some PDF graphics parameters}%
[\entrysep]
\entry{pdftexcmds}{2019/07/25}{0.30}{Utility functions of \hologo{pdfTeX} for \hologo{LuaTeX}}%
[\entrysep]
>>>>>>> master:oberdiek.tex
\entry{picture}{2009/10/11}{1.3}{Dimens for picture macros}%
[\entrysep]
\entry{pmboxdraw}{2011/03/24}{1.1}{Poor man's box drawing characters}%
[\entrysep]
\entry{refcount}{2011/10/16}{3.4}{Data extraction from label references}%
[\entrysep]
\entry{rerunfilecheck}{2011/04/15}{1.7}{Rerun checks for auxiliary files}%
[\entrysep]
\entry{resizegather}{2010/03/01}{1.2}{Resize overly large equations}%
[\entrysep]
\entry{scrindex}{2008/08/11}{1.1}{Package index with \hologo{KOMAScript} classes}%
[\entrysep]
\entry{settobox}{2008/08/11}{1.4}{Assign box dimensions to length registers}%
[\entrysep]
\entry{soulutf8}{2007/09/09}{1.0}{Permit use of UTF-8 characters in soul}%
[\entrysep]
\entry{stackrel}{2007/11/11}{1.2}{Adding subscript option to stackrel}%
[\entrysep]
\entry{stampinclude}{2008/07/14}{1.0}{Include files based on time stamps}%
[\entrysep]
\entry{tabularht}{2007/04/11}{2.5}{Tabular with height specified}%
[\entrysep]
\entry{tabularkv}{2006/02/20}{1.1}{Tabular with key value interface}%
[\entrysep]
\entry{telprint}{2008/08/11}{1.10}{Format German phone numbers}%
[\entrysep]
\entry{transparent}{2007/01/08}{1.0}{Transparency via \hologo{pdfTeX}'s color stack}%
[\entrysep]
\entry{twoopt}{2008/08/11}{1.5}{Definitions with two optional arguments}%
\end{overview}

\section{Packages}
\hypersetup{bookmarksnumbered=false}

\subsection{\pkgsectformat{accsupp}}
\label{accsupp}
\begin{abstract}
Since PDF 1.5 portions of a page can be marked for better
accessibility support.
For example, replacement texts or expansions of abbreviations can be
provided. Package \xpackage{accsupp} starts with providing a minimal
low-level interface for programmers. Status is experimental.
\end{abstract}
\tocinclude{accsupp}

\newpage
\subsection{\pkgsectformat{aliascnt}}
\label{aliascnt}
\begin{abstract}
Package \xpackage{aliascnt} introduces \emph{alias counters} that
share the same counter register and clear list.
\end{abstract}
\tocinclude{aliascnt}


\newpage
\subsection{\pkgsectformat{askinclude}}
\label{askinclude}
\begin{abstract}
This package replaces \cs{includeonly} by an interactive user
interface.
\end{abstract}
\tocinclude{askinclude}


\newpage
\subsection{\pkgsectformat{atenddvi}}
\label{atenddvi}
\begin{abstract}
\LaTeX\ offers \cs{AtBeginDvi}. This package \xpackage{atenddvi}
provides the counterpart \cs{AtEndDvi}. The execution of its
argument is delayed to the end of the document at the end of the
last page. Thus \cs{special} and \cs{write} remain effective, because
they are put into the last page. This is the main difference
to \cs{AtEndDocument}.
\end{abstract}
\tocinclude{atenddvi}

\newpage
\subsection{\pkgsectformat{attachfile2}}
\label{attachfile2}
\begin{abstract}
This package can be used to attach files to a PDF document.
It is a further development of Scott Pakin's package
\xpackage{attachfile} for \pdfTeX. Apart from bug fixes,
package \xpackage{attachfile2} adds support for \xoption{dvips},
some new options, gets and writes meta information data about
the attached files.
\end{abstract}
\tocinclude{attachfile2}

\newpage
\subsection{\pkgsectformat{atveryend}}
\label{atveryend}
\begin{abstract}
This \LaTeX\ package provides two hooks for \verb|\end{document}|
that are executed after the hook of \cs{AtEndDocument}.
\cs{AfterLastShipout} can be used for code that is to be executed
right after the last \cs{clearpage} before the \xext{aux} file
is closed. \cs{AtVeryEndDocument} is used for code after closing
and final reading of the \xext{aux} file.
\end{abstract}
\tocinclude{atveryend}

\newpage
\subsection{\pkgsectformat{auxhook}}
\label{auxhook}
\begin{abstract}
Package \xpackage{auxhook} provides hooks for adding stuff at
the begin of \xfile{.aux} files.
\end{abstract}
\tocinclude{auxhook}


\newpage
\subsection{\pkgsectformat{bmpsize}}
\label{bmpsize}
\begin{abstract}
Package \xpackage{bmpsize} analyzes bitmap images to extract
size and resolution data. It adds this feature to the graphics package
that now do not need separate bounding box files for bitmap images.
Additionally the implementation for the inclusion of bitmap images
in some drivers of package \xpackage{graphicx} are rewritten to support
options \xoption{viewport}, \xoption{trim} and \xoption{clip}.
\end{abstract}
\tocinclude{bmpsize}

\newpage
\subsection{\pkgsectformat{bookmark}}
\label{bookmark}
\begin{abstract}
This package implements a new bookmark (outline) organization for
package \xpackage{hyperref}. Bookmark properties such
as style and color can now be set. Other action types
are available (URI, GoToR, Named). The bookmarks are
generated in the first compile run. Package \xpackage{hyperref}
uses two runs.
\end{abstract}
\tocinclude{bookmark}

\newpage
\subsection{\pkgsectformat{centernot}}
\label{centernot}
\begin{abstract}
This package provides \cs{centernot} that prints the symbol
\cs{not} on the following argument. Unlike \cs{not} the symbol
is horizontally centered.
\end{abstract}
\tocinclude{centernot}

\newpage
\subsection{\pkgsectformat{chemarr}}
\label{chemarr}
\begin{abstract}
Very often chemists need a longer version
of reaction arrows (\cs{rightleftharpoons}) with
the possibility to put text above and below.
Analogous to \xpackage{amsmath}'s \cs{xrightarrow} and
\cs{xleftarrow} this package provides the macro
\cs{xrightleftharpoons}.
\end{abstract}
\tocinclude{chemarr}

\newpage
\subsection{\pkgsectformat{classlist}}
\label{classlist}
\begin{abstract}
This package records the loaded classes and stores
them in a list.
\end{abstract}
\tocinclude{classlist}

\newpage
\subsection{\pkgsectformat{colonequals}}
\label{colonequals}
\begin{abstract}
Package \xpackage{colonequals} defines poor man's symbols
for math relation symbols such as ``colon equals''.
The colon is centered around the horizontal math axis.
\end{abstract}
\tocinclude{colonequals}

\newpage
\subsection{\pkgsectformat{dvipscol}}
\label{dvipscol}
\begin{abstract}
Color support for dvips in \xfile{dvips.def} involves the
color stack of dvips. The package tries to remove unnecessary
uses of the stack to avoid the error ``out of coor stack space''.
\end{abstract}
\tocinclude{dvipscol}


\newpage
\subsection{\pkgsectformat{enparen}}
\label{enparen}
\begin{abstract}
The package defines macros to set parentheses that automatically
change the symbols from inner to outer fences.
\end{abstract}
\tocinclude{enparen}


\newpage
\subsection{\pkgsectformat{epstopdf}}
\label{epstopdf}
\begin{abstract}
This packages adds support of handling eps images
to package \xpackage{graphics} or \xpackage{graphicx}
with option \xoption{pdftex}. If an eps image is detected,
epstopdf is automatically called to convert it to pdf format.
\end{abstract}
\tocinclude{epstopdf}


\newpage
\subsection{\pkgsectformat{flags}}
\label{flags}
\begin{abstract}
Package \xpackage{flags} allows the setting and clearing
of flags in bit fields and converts the bit field into a
decimal number. Currently the bit field is limited to 31 bits.
\end{abstract}
\tocinclude{flags}


\newpage
\subsection{\pkgsectformat{grfext}}
\label{grfext}
\begin{abstract}
This package provides macros for adding and reordering
graphics extensions of package \xpackage{graphics}.
\end{abstract}
\tocinclude{grfext}

\newpage
\subsection{\pkgsectformat{grffile}}
\label{grffile}
\begin{abstract}
The package extends the file name processing of package \xpackage{graphics}
to support a larger range of file names. For example, the file name
may contain several dots. Or in case of \pdfTeX\ in PDF mode the file name may
contain spaces.
\end{abstract}
\tocinclude{grffile}


\newpage
\subsection{\pkgsectformat{holtxdoc}}
\label{holtxdoc}
\begin{abstract}
The package is used for the documentation of my packages in
DTX format. It contains some private macros and setup for
my needs. Thus do not use it. I have separated the part
that may be useful for others in package \xpackage{hypdoc}.
\end{abstract}
\tocinclude{holtxdoc}

\newpage
\subsection{\pkgsectformat{hopatch}}
\label{hopatch}
\begin{abstract}
This packages provides a wrapper to various package hooks
provided by other packages or classes, but does not define
own hooks.
\end{abstract}
\tocinclude{hopatch}



\newpage
\subsection{\pkgsectformat{ifdraft}}
\label{ifdraft}
\begin{abstract}
The package provides an interface for selecting code depending
on the options \xoption{draft} and \xoption{final}.
\end{abstract}
\tocinclude{ifdraft}


\newpage
\subsection{\pkgsectformat{inputenx}}
\label{inputenx}
\begin{abstract}
This package provides input encodings using
standard mappings and covers nearly all slots. Thus it
serves as more uptodate replacement for package \xpackage{inputenc}.
\end{abstract}
\tocinclude{inputenx}


\newpage
\subsection{\pkgsectformat{letltxmacro}}
\label{letltxmacro}
\begin{abstract}
\TeX's \cs{let} assignment does not work for \LaTeX\ macros
with optional arguments or for macros that are defined
as robust macros by \cs{DeclareRobustCommand}. This package
defines \cs{LetLtxMacro} that also takes care of the involved
internal macros.
\end{abstract}
\tocinclude{letltxmacro}

\newpage
\subsection{\pkgsectformat{listingsutf8}}
\label{listingsutf8}
\begin{abstract}
Package \xpackage{listings} does not support files with multi-byte
encodings such as UTF-8. In case of \cs{lstinputlisting} a simple
workaround is possible if an one-byte encoding exists that the file
can be converted to. Also \eTeX\ and \pdfTeX\ regardless of its mode
are required.
\end{abstract}
\tocinclude{listingsutf8}


\newpage
\subsection{\pkgsectformat{luacolor}}
\label{luacolor}
\begin{abstract}
Package \xpackage{luacolor} implements color support based
on \LuaTeX's node attributes.
\end{abstract}
\tocinclude{luacolor}



\newpage
\subsection{\pkgsectformat{makerobust}}
\label{makerobust}
\begin{abstract}
Package \xpackage{makerobust} provides \cs{MakeRobustCommand}
that converts an existing macro to a robust one.
\end{abstract}
\tocinclude{makerobust}


\newpage
\subsection{\pkgsectformat{pagegrid}}
\label{pagegrid}
\begin{abstract}
The \LaTeX\ package prints a page grid in the background.
\end{abstract}
\tocinclude{pagegrid}

\newpage
\subsection{\pkgsectformat{pagesel}}
\label{pagesel}
\begin{abstract}
Single pages or page areas can be selected for output.
\end{abstract}
\tocinclude{pagesel}



\newpage
\subsection{\pkgsectformat{pdflscape}}
\label{pdflscape}
\begin{abstract}
Package \xpackage{pdflscape} adds PDF support to the
environment \texttt{landscape} of package \xpackage{lscape}
by setting the PDF page attribute \texttt{/Rotate}.
\end{abstract}
\tocinclude{pdflscape}


\newpage
\subsection{\pkgsectformat{picture}}
\label{picture}
\begin{abstract}
There are macro and environment arguments that expect numbers
that will internally be multiplicated with \cs{unitlength}.
This package extends the syntax of these arguments that
dimens with calculation support can be added for these arguments.
\end{abstract}
\tocinclude{picture}

\newpage
\subsection{\pkgsectformat{pmboxdraw}}
\label{pmboxdraw}
\begin{abstract}
Package \xpackage{pmboxdraw} declares box drawings characters of
old code pages, e.g. cp437. It uses rules instead of using a font.
\end{abstract}
\tocinclude{pmboxdraw}


\newpage
\subsection{\pkgsectformat{refcount}}
\label{refcount}
\begin{abstract}
References are not numbers, however they often store numerical
data such as section or page numbers. \cs{ref} or \cs{pageref}
cannot be used for counter assignments or calculations because
they are not expandable, generate warnings, or can even be links.
The package provides expandable macros to extract the data
from references. Packages \xpackage{hyperref}, \xpackage{nameref},
\xpackage{titleref}, and \xpackage{babel} are supported.
\end{abstract}
\tocinclude{refcount}

\newpage
\subsection{\pkgsectformat{rerunfilecheck}}
\label{rerunfilecheck}
\begin{abstract}
The package provides additional rerun warnings if some
auxiliary files have changed. It is based on MD5 checksum,
provided by \pdfTeX.
\end{abstract}
\tocinclude{rerunfilecheck}

\newpage
\subsection{\pkgsectformat{resizegather}}
\label{resizegather}
\begin{abstract}
Equations that are too large are resized to fit the available
space. The environment \textsf{gather} of package \xpackage{amsmath}
is supported. Also the environments \textsf{equation} and
\textsf{displaymath} are redefined using \textsf{gather}
and its starred version.
\end{abstract}
\tocinclude{resizegather}


\newpage
\subsection{\pkgsectformat{scrindex}}
\label{scrindex}
\begin{abstract}
This package redefines environment `theindex' of package \xpackage{index},
if a class from KOMA-Script is loaded. Also option \xoption{idxtotoc}
is supported. Index preambles can be given either by means of package
\xpackage{index} or via the interface provided by KOMA-Script.
\end{abstract}
\tocinclude{scrindex}


\newpage
\subsection{\pkgsectformat{settobox}}
\label{settobox}
\begin{abstract}
Commands are defined for getting box sizes similar
to \LaTeX's \cs{settowidth} commands.
\end{abstract}
\tocinclude{settobox}

\newpage
\subsection{\pkgsectformat{soulutf8}}
\label{soulutf8}
\begin{abstract}
This package extends package \xpackage{soul} and adds some support
for UTF-8. Namely the input encodings \xfile{utf8.def}
from package \xpackage{inputenc} and
package \xpackage{ucs}'s \xfile{utf8x.def} are supported.
\end{abstract}
\tocinclude{soulutf8}

\newpage
\subsection{\pkgsectformat{stackrel}}
\label{stackrel}
\begin{abstract}
This package adds an optional argument to \cs{stackrel} for
putting something below the relational symbol and defines
\cs{stackbin} for binary symbols.
\end{abstract}
\tocinclude{stackrel}

\newpage
\subsection{\pkgsectformat{stampinclude}}
\label{stampinclude}
\begin{abstract}
The package replaces \cs{includeonly} and selects the files for
\cs{include} by inspecting the time stamp of the \xext{aux} file.
The file is selected for inclusion if the \xext{aux} file does
not yet exist or is older than the corresponding \xext{tex} file.
\end{abstract}
\tocinclude{stampinclude}


\newpage
\subsection{\pkgsectformat{tabularht}}
\label{tabularht}
\begin{abstract}
This package defines some environments that adds
a height specification to tabular and array.
\end{abstract}
\tocinclude{tabularht}

\newpage
\subsection{\pkgsectformat{tabularkv}}
\label{tabularkv}
\begin{abstract}
This package adds a key value interface for tabular
by the new environment \texttt{tabularkv}. Thus the
\TeX\ source code looks better by named parameters,
especially if package \xpackage{tabularht} is used.
\end{abstract}
\tocinclude{tabularkv}

\newpage
\subsection{\pkgsectformat{telprint}}
\label{telprint}
\begin{abstract}
Package \xpackage{telprint} provides \cs{telprint} for formatting
German phone numbers.
\end{abstract}
\tocinclude{telprint}


\newpage
\subsection{\pkgsectformat{transparent}}
\label{transparent}
\begin{abstract}
Since version 1.40 \pdfTeX\ supports several color stacks. This
package shows, how a separate color stack can be used for transparency,
a property besides color.
\end{abstract}
\tocinclude{transparent}

\newpage
\subsection{\pkgsectformat{twoopt}}
\label{twoopt}
\begin{abstract}
This package provides commands to define macros with two
optional arguments.
\end{abstract}
\tocinclude{twoopt}


\end{document}
